Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method

### 2019-09-25 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

In this section, we present the theory and methodology created to obtain the optimal sizing of stand-alone solar PV systems through program synthesis.

\textcolor{red}{Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, showing the traditional techniques (manual and simulation), and including the proposed automatic synthesis. Worth to mention that the input information is the same for all the methods (weather data, detailed equipment and price information, design requirements, as load curve and power demand, and design assumptions), with the difference that in automated synthesis is possible to define the bound $k$ to restrict the design-space search. Related to the output presented by the techniques, all produce a successful or fail result considering a feasible technical solution that has the lowest cost. However when done by simulation we get a report or graphical result; in the other hand, the automated synthesis technique, that is a mathematical reasoning of a model, presents a counter-example with the optimal solution stored in variables. Furthermore, as it will be showed in this section, the design-space coverage during the optimal sizing search is more complete when using automated synthesis.}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{optimalsizingprocess3}
\centering
\caption{Comparative of optimal sizing methods.}
\label{fig:optimization}
\end{figure}

>>>>

In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis. In particular, Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis. Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions) except for the automated synthesis where we also define the bound $k$ to restrict the design-space search. Related to the output presented by both techniques, all of them produce a successful or fail result considering a feasible technical solution with the lowest cost. On the one hand, when done by simulation we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables. Furthermore, as described in this section, the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.
%
\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{optimalsizingprocess3}
\centering
\caption{Comparative of optimal sizing methods.}
\label{fig:optimization}
\end{figure}
